A Hybrid Ensemble Learning Approach to Star-Galaxy Classification

### 2015-05-08 paper/main.tex
minor typo - third person singular of have = has

\begin{table*}
  \caption{A summary of the classification performance metrics
           for the four individual methods
           and the four different classification combination methods
           when the training data set consists of
           only the sources that are in CFHTLS W1 field,
           have spectroscopic labels available from VVDS,
           and have $i < 22$.
           The definition of the metrics is summarized in
           Table~\ref{table:metrics}.
           The bold entries highlight the best performance values
           within each column.}
  \centering
  \input{tables/metrics_cut.tex}
  \label{table:metrics_cut}
\end{table*}

>>>>

\begin{table*}
  \caption{A summary of the classification performance metrics
           for the four individual methods
           and the four different classification combination methods
           when the training data set consists of
           only the sources that are in CFHTLS W1 field,
           has spectroscopic labels available from VVDS,
           and has $i < 22$.
           The definition of the metrics is summarized in
           Table~\ref{table:metrics}.
           The bold entries highlight the best performance values
           within each column.}
  \centering
  \input{tables/metrics_cut.tex}
  \label{table:metrics_cut}
\end{table*}
